Fractional anisotropy as an optimal tracer of cosmic voids

### 2014-08-12 cosmic_voids.tex
Simulation section and other references

We use here an unconstrained cosmological simulation, the Bolshoi 
simulation, to identify the possible large scale environment and 
cosmological voids.

The Bolshoi simulation follows the non-linear evolution of a dark matter 
density field on a cubic volume of size $250$\hMpc sampled with $2048^3$ 
particles. The cosmological parameters in the simulation are 
$\Omega_{\rm m}=0.27$, $\Omega_{\Lambda}=0.73$, $h=0.70$, $n=0.95$ and 
$\sigma_{8}=0.82$ for the matter density, cosmological constant, 
dimensionless Hubble parameter, spectral index of primordial density 
perturbations and normalization for the power spectrum. The mass of each 
particle in the simulation is $m_{\rm p}=1.4\times 10^{8}$\hMsun.
We identify catalogues of halos through the Bound Density Maximum 
algorithm.

>>>>

We use here an unconstrained cosmological simulation (the Bolshoi 
simulation) to identify the possible large scale environment and the 
distribution of cosmic voids at $z=0$. The Bolshoi simulation follows the 
non-linear evolution of a dark matter density field on a cubic volume of 
size $250$\hMpc sampled with $2048^3$ particles. The cosmological 
parameters in the simulation are $\Omega_{\rm m}=0.27$, $\Omega_{\Lambda}
=0.73$, $h=0.70$, $n=0.95$ and $\sigma_{8}=0.82$ for the matter density, 
cosmological constant, dimensionless Hubble parameter, spectral index of 
primordial density perturbations and normalization for the power spectrum
respectively, consistent with the seventh year of data of the Wilkinson 
Microwave Anisotropy Probe (WMAP) \citep{Jarosik11}. For more detailed 
technical information about the simulation, see \citet{Klypin11}.

With the above parameters the mass of each particle in the simulation is 
$m_{\rm p}=1.4\times 10^{8}$\hMsun. Throughout this paper we shall use a
catalogue of halos identified through the Bound Density Maximum algorithm
\citep{Klypin99}. These halos have been selected to have an overdensity of
200 times the critical density in addition to be mutually excluded of the
virial radius of other halos. Mass, comoving position and peculiar 
velocity of each halo at $z=0$ were obtained through the public available 
Multidark database \footnote{\url{http://www.multidark.org/MultiDark/}} 
\citep{Riebe11}. For estimating the density and velocity fields we use a 
\textit{cloud-in-cell} (\texttt{CIC}) algorithm onto a grid of $256^3$ 
cells, corresponding to a resolution of $0.98$\hMpc per cell side. Then, 
through a finite-difference scheme, the tidal and shear tensors are 
computed. Finally the eigenvalues and eigenvectors of each tensor are 
obtained for each cell of the grid. Neglecting substructures presented 
below Megaparsec scales and taking into account our focus in voids, which 
are a prominent characteristic of the Megaparsec Universe, we apply a 
Gaussian softening of one cell to all our fields.
